Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-04 RR_manuscript/Draft_RR.Rmd
remove spurious sentence from ## Step 5
expand exploration variables list (closes #15)

- *Measure of uniqueness* of individual analyses for the set of predictors in each model.
- *Measure of conservativeness* of the model specification.
- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out.
- *Number of models* the teams will report to have run.
- *Major dimension* that has been measured to answer the research question.
- *Temporal window* that the measurement is taken over.
- *Demographic factors* of analysis teams and analysts.

@@

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package (Baselga et al. 2018).
The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g. frequency center of gravity, harmonics difference, etc.), other measures (e.g. principal components, vowel dispersion, etc.)
<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

@@

- ...

@@

We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).

>>>>

- *Measure of uniqueness* of individual analyses for the set of predictors in each model.
- *Measure of conservativeness* of the model specification.
- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out.
- *Number of models* the teams will report to have run.
- *Major dimension* that has been measured to answer the research question.
- *Temporal window* that the measurement is taken over.
- *Data exclusion*, whether data has been excluded or not.
- *Demographic factors* of analysis teams and analysts.

@@

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package (Baselga et al. 2018).

The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g. frequency center of gravity, harmonics difference, etc.), other measures (e.g. principal components, vowel dispersion, etc.)
<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

@@

- *Research experience* as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.

@@
